---
title: "Housing Prices in the DC metro area"
author: "Anna Vasylytsya"
date: "11/8/2019"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, 
                      warning = FALSE, error = FALSE)
```

```{r packages}
library(geosphere)
library(stargazer)
library(mapdeck)
```

```{r path, echo = FALSE}
proj_path <- "C:/Users/Anna V/Documents/GitHub/housing_radius"
```

```{r token, echo = FALSE}
my_token <- scan(paste0(proj_path, "/_auth/mapbox_token.txt"), 
                 character(), quote = "")
mapdeck::set_token(my_token)
```

# Background and Description
```{r load_all_data}
data <- read.csv(paste0(proj_path, "/data/02_redfin_clean_all.csv"), 
                 header = TRUE, stringsAsFactors = FALSE)
```

This data was manually downloaded from Redfin on September 16th, 2019, therefore the data covers listings on that date. These listings cover `r length(unique(data$zip_code))` zipcodes in DC, Maryland, and Virginia.

This dataset contains `r format(nrow(data), big.mark=",")` listings. The average listing price is \$`r format(round(mean(data$price, na.rm = TRUE), digit = 0), big.mark=",")`. The average listing square footage is `r format(round(mean(data$square.feet, na.rm = TRUE), digit = 0), big.mark = ",")`. The most expensive property was listed for \$`r format(max(data$price), big.mark = ",")`. The largest property listed had `r format(max(data$square.feet, na.rm = TRUE), big.mark = ",")` square feet.

There are `r format(nrow(data[data$price<5000000, ]), big.mark = ",")` listings that are below \$2 million. For listings under two million dollars, the average listing price is \$ `r format(round(mean(data[data$price<5000000,  "price"], na.rm = TRUE), digit = 0), big.mark = ",")` and the average listing square footage is `r format(round(mean(data[data$price<5000000,  "square.feet"], na.rm = TRUE), digit = 0), big.mark = ",")`.

```{r subset_data}
data <- data[ , c("property.type", "price", "square.feet", "price_per_sq_ft","latitude", "longitude", "url")]

price <- data[ , c("property.type", "price", "latitude", "longitude")]  
names(price)[1] <- "Property Type"
price_u2m <- price[price$price < 2000000, ]

sqft <- data[ , c("property.type", "price", "square.feet", "latitude", "longitude")]  
  names(sqft)[1] <- c("Property Type")
sqft_u2m_price <- sqft[sqft$price < 2000000, ]
sqft <- sqft[ , c("Property Type", "square.feet", "latitude", "longitude")]  

price_sqft <- data[ , c("property.type", "price","price_per_sq_ft", "latitude", "longitude")]  
  names(price_sqft)[1] <- c("Property Type")
price_sqft_u2m <- price_sqft[price_sqft$price < 2000000, ]
price_sqft <- price_sqft[ , c("Property Type", "price_per_sq_ft", "latitude", "longitude")]  
```

```{r dist_matrix}
#coordinate for US Capitol
capitol <- c(-77.008991, 38.890089)

# create distance matrix from each listing to the US Capitol (units = meters)
dist_m <- distm(data[ c("longitude", "latitude")], capitol, fun =  distGeo)
  
# add to dataframe and convert to kilometers
data$dist_km <- (dist_m/1000)

rm(dist_m)
```

# Listing Price 
### All Listings
```{r all_price_reg}
lm_price_all <- lm(price ~ dist_km, data = data)
lm_price_condo <- lm(price ~ dist_km, data = data[data$property.type == "Condo/Co-op", ])
lm_price_town <- lm(price ~ dist_km, data = data[data$property.type == "Townhouse", ])
lm_price_house <- lm(price ~ dist_km, data = data[data$property.type == "Single Family Residential" 
                                                  | data$property.type == "Multi-Family (2-4 Unit)", ])
```

```{r all_price_reg_results}
stargazer(lm_price_all, lm_price_condo, lm_price_town,lm_price_house, 
          type = "text", digits = 1, 
          column.labels = c("All", "Condo", "Townhouse", "House"), 
          covariate.labels = "Distance from US Capitol in km", 
          dep.var.labels   = "List Price",
          omit.stat = c("f", "ser", "rsq") )
```

```{r all_price_map}
# mapdeck(
#   style = mapdeck_style('light')) %>%
#   add_column(
#     data = price
#     , lat = "latitude"
#     , lon = "longitude"
#     , radius = 75
#     , elevation = "price"
#     , elevation_scale = 0.001
#     , layer_id = "price"
#     , auto_highlight = TRUE
#     , update_view = TRUE
#     , fill_colour = "Property Type"
#     , fill_opacity = 0.65
#     , tooltip = "price"
#     , legend = TRUE) %>%
#   mapdeck_view(location = c(-77.008989, 38.890468), pitch = 60, zoom = 9)  
```

### Listings under $2 million
```{r price_under2M_reg}
lm_price_all2 <- lm(price ~ dist_km, data = data[data$price <2000000, ])
lm_price_condo2 <- lm(price ~ dist_km, data = data[data$property.type == "Condo/Co-op" & data$price <2000000, ])
lm_price_town2 <- lm(price ~ dist_km, data = data[data$property.type == "Townhouse" & data$price <2000000, ])
lm_price_house2 <- lm(price ~ dist_km, data = data[(data$property.type == "Single Family Residential" 
                                                    | data$property.type == "Multi-Family (2-4 Unit)") & data$price <2000000, ])

stargazer(lm_price_all2, lm_price_condo2, lm_price_town2,lm_price_house2, 
          type = "text", digits = 1, 
          column.labels = c("All <2M", "Condo <2M", "Townhouse <2M", "House <2M"), 
          covariate.labels = "Distance from US Capitol in km", 
          dep.var.labels   = "List Price",
          omit.stat = c("f", "ser", "rsq") )
```

```{r price_under2M_reg_results}
```

```{r price_under2M_map}

```

# Square Feet
### All Listings
```{r all_sqft_reg}
lm_sqft_all <- lm(square.feet ~ dist_km, data = data)
lm_sqft_condo <- lm(square.feet ~ dist_km, data = data[data$property.type == "Condo/Co-op", ])
lm_sqft_town <- lm(square.feet ~ dist_km, data = data[data$property.type == "Townhouse", ])
lm_sqft_house <- lm(square.feet ~ dist_km, data = data[data$property.type == "Single Family Residential" 
                                                       | data$property.type == "Multi-Family (2-4 Unit)", ])

stargazer(lm_sqft_all, lm_sqft_condo, lm_sqft_town,lm_sqft_house, 
          type = "text", digits = 1, 
          column.labels = c("All", "Condo", "Townhouse", "House"), 
          covariate.labels = "Distance from US Capitol in km", 
          dep.var.labels   = "Listing Square Feet",
          omit.stat = c("f", "ser", "rsq") )
```

```{r all_sqft_reg_results}
```

```{r all_sqft_map}

```

### Listings under $2 million
```{r sqft_under2M_reg}
lm_sqft_all2 <- lm(square.feet ~ dist_km, data = data[data$price <2000000, ])
lm_sqft_condo2 <- lm(square.feet ~ dist_km, data = data[data$property.type == "Condo/Co-op" & data$price <2000000, ])
lm_sqft_town2 <- lm(square.feet ~ dist_km, data = data[data$property.type == "Townhouse" & data$price <2000000, ])
lm_sqft_house2 <- lm(square.feet ~ dist_km, data = data[(data$property.type == "Single Family Residential" 
                                                        | data$property.type == "Multi-Family (2-4 Unit)") 
                                                        & data$price <2000000, ])

stargazer(lm_sqft_all2, lm_sqft_condo2, lm_sqft_town2,lm_sqft_house2, 
          type = "text", digits = 1, 
          column.labels = c("All", "Condo", "Townhouse", "House"), 
          covariate.labels = "Distance from US Capitol in km", 
          dep.var.labels   = "Listing Square Feet",
          omit.stat = c("f", "ser", "rsq") )
```

```{r sqft_under2M_reg_results}
```

```{r sqft_under2M_map}

```

# Price per Square Foot

### All Listings
```{r all_psqft_reg}
lm_psqft_all <- lm(price_per_sq_ft ~ dist_km, data = data)
lm_psqft_condo <- lm(price_per_sq_ft ~ dist_km, data = data[data$property.type == "Condo/Co-op", ])
lm_psqft_town <- lm(price_per_sq_ft ~ dist_km, data = data[data$property.type == "Townhouse", ])
lm_psqft_house <- lm(price_per_sq_ft ~ dist_km, data = data[data$property.type == "Single Family Residential" 
                                                            | data$property.type == "Multi-Family (2-4 Unit)", ])

stargazer(lm_psqft_all, lm_psqft_condo, lm_psqft_town,lm_psqft_house, 
          type = "text", digits = 1, 
          column.labels = c("All", "Condo", "Townhouse", "House"), 
          covariate.labels = "Distance from US Capitol in km", 
          dep.var.labels   = "Price per Square Foot",
          omit.stat = c("f", "ser", "rsq") )
```

```{r all_psqft_reg_results}
```

```{r all_psqft_map}

```

### Listings under $2 million
```{r psqft_under2M_reg}
lm_psqft_all2 <- lm(price_per_sq_ft ~ dist_km, data = data[data$price <2000000, ])
lm_psqft_condo2 <- lm(price_per_sq_ft ~ dist_km, data = data[data$property.type == "Condo/Co-op" & data$price <2000000, ])
lm_psqft_town2 <- lm(price_per_sq_ft ~ dist_km, data = data[data$property.type == "Townhouse" & data$price <2000000, ])
lm_psqft_house2 <- lm(price_per_sq_ft ~ dist_km, data = data[(data$property.type == "Single Family Residential"
                                                              | data$property.type == "Multi-Family (2-4 Unit)") & data$price <2000000, ])

stargazer(lm_psqft_all2, lm_psqft_condo2, lm_psqft_town2,lm_psqft_house2, 
          type = "text", digits = 1, 
          column.labels = c("All", "Condo", "Townhouse", "House"), 
          covariate.labels = "Distance from US Capitol in km", 
          dep.var.labels   = "Price per Square Foot",
          omit.stat = c("f", "ser", "rsq") )
```

```{r psqft_under2M_reg_results}
```

```{r psqft_under2M_map}

```
